Fusion Moves for Correlation Clustering

### 2014-10-27 paper/egpaper_for_review.tex
update
polytope pic
polyhedral intepreation

\usepackage{tkz-berge}
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}
\definecolor{shadecolor}{rgb}{0.01,0.199,0.1}
\usepackage{xargs} 
\newtheorem{theorem}{Theorem}

@@

\subsection{Polyhedral Interpretation}

@@

\subsection{Benchmark Models}

@@

\subsection{Pixel-wise Multicuts}
\input{inputs/fig_pixel_mc.tex}

@@

{\small
\bibliographystyle{ieee}
\bibliography{egbib}
}

>>>>

%\usepackage{tkz-berge}
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}
\definecolor{shadecolor}{rgb}{0.01,0.199,0.1}
\usepackage{xargs} 
\newtheorem{theorem}{Theorem}

@@

\subsection{Polyhedral Interpretation}
\begin{figure}
\centering
\input{polytope-tikz.tex}
\caption{Each move can be interpreted as an optimization of an inner polyhedral optimization.
Each polyhedral approximation includes the current vertex. Starting with $y_0$ we optimize over the red polytope 
and find $y_1$ as optima. When optimize over the blue polytope we stay in $y_1$ as optima.
When optimizing over the green polytope we find $y_2$ which we will never leaf again or any polytope containing $y_2$. 
}
\end{figure}

@@

\subsection{Synthetic Models}

\subsection{Real World Models}

@@

%\subsection{Pixel-wise Multicuts}
%\input{inputs/fig_pixel_mc.tex}

@@

\newpage
{\small
\bibliographystyle{ieee}
\bibliography{egbib}
}
